Developing ShinyMICE

### 2019-12-16 Presentation/Presentation_Hanne.Rmd

## This presentation | and the entire research archive is available on:

<center>
[github.com/gerkovink/ShinyMICE/](https://github.com/gerkovink/ShinyMICE/)
</center>
<br><br><br>
You can find all related materials, links and references there.

## Content of the Presentation

<div class="columns-2">
<img src="figures/shinymice.png" alt="HTML5 Icon" width = 110%>

<br><br><br>

- Introduction
- Methodology
- Simulation Results
- Discussion
</div>

# Introduction

## Multiple imputation
- Missing data is ubiquitous [@alli02]. 
- *Ad hoc* solutions may yield invalid inferences [@buur18].
- @rubin87 proposed the framework of MI.

@@

# Methodology

## Mock code | 
Steps in the simulation study
```{r eval=FALSE}
simulation <- function() {
  mvtnorm(X,Z1,Z2) %>% 
  mutate(Y~X+Z1+Z2) %>% 
  for (max_iterations in 1:100) {
    ampute() %>% 
    impute() %T% 
    convergence_diagnostics %>% 
    lm(Y~X+Z1+Z2) %>% 
    pool %>% 
    simulation_diagnostics %>% 
    c(., convergence_diagnostics)
  }
}

replicate(simulation, n = 1000)
```

# Simulation Results

## Simulation diagnostics
<center>
<img src="figures/results_sim.png" alt="HTML5 Icon" width = 100%>
<br>

@@

## Convergence diagnostics
<center>
<img src="figures/results_conv.png" alt="HTML5 Icon" width = 100%>
<br>

@@

## Inspect the autocorrelation dip
```{r echo=FALSE}
dat %>% round(3) %$%  plot_ly(x = It., y = AC_mean_X, 
        text = paste("R hat: ", R_mean_X),
        type = "scatter", mode = "lines") %>% 
  layout(#title = "Auto-correlation across iterations",
         xaxis = list(title = "Nr. of iterations"),
         yaxis = list(title = "Auto-correlation (at lag 1)"))
```

# Discussion

>>>>

<!-- ## This presentation | and the entire research archive is available on:  -->

<!-- <center> -->
<!-- [github.com/gerkovink/ShinyMICE/](https://github.com/gerkovink/ShinyMICE/) -->
<!-- </center> -->
<!-- <br><br><br> -->
<!-- You can find all related materials, links and references there.  -->

<!-- ## Content of the Presentation -->

<!-- <div class="columns-2"> -->
<!-- <img src="figures/shinymice.png" alt="HTML5 Icon" width = 110%> -->

<!-- <br><br><br> -->

<!-- - Introduction -->
<!-- - Methodology -->
<!-- - Simulation Results -->
<!-- - Discussion -->
<!-- </div> -->

<!-- # Introduction -->

<!-- ## Multiple imputation -->
<!-- - Missing data is ubiquitous [@alli02].  -->
<!-- - *Ad hoc* solutions may yield invalid inferences [@buur18]. -->
<!-- - @rubin87 proposed the framework of MI. -->

@@

<!-- # Methodology -->

<!-- ## Mock code -->
<!-- ```{r eval=FALSE} -->
<!-- simulation <- function() { -->
<!--   mvtnorm(X,Z1,Z2) %>%  -->
<!--   mutate(Y~X+Z1+Z2) %>%  -->
<!--   for (max_iterations in 1:100) { -->
<!--     ampute() %>%  -->
<!--     impute() %T%  -->
<!--     convergence_diagnostics %>%  -->
<!--     lm(Y~X+Z1+Z2) %>%  -->
<!--     pool %>%  -->
<!--     simulation_diagnostics %>%  -->
<!--     c(., convergence_diagnostics) -->
<!--   } -->
<!-- } -->

<!-- replicate(simulation, n = 1000) -->
<!-- ``` -->

<!-- # Simulation Results -->

## Results: simulation diagnostics
<center>
<img src="figures/results_sim.png" alt="HTML5 Icon" width = 100%>
<br>

@@

## Results: convergence diagnostics
<center>
<img src="figures/results_conv.png" alt="HTML5 Icon" width = 100%>
<br>

@@

<!-- ## Results | Simulation diagnostics versus convergence diagnostics -->
<!-- ```{r echo=FALSE} -->
<!-- dat %>% select("It.", "bias", "CIW", "cov", "R_mean_X", "AC_mean_X") %>% round(3) %>% datatable(options = list(pageLength = 5), rownames = FALSE) -->
<!-- ``` -->

<!-- ## Inspect the autocorrelation dip -->
<!-- ```{r echo=FALSE} -->
<!-- dat %>% round(3) %$%  plot_ly(x = It., y = AC_mean_X,  -->
<!--         text = paste("R hat: ", R_mean_X), -->
<!--         type = "scatter", mode = "lines") %>%  -->
<!--   layout(#title = "Auto-correlation across iterations", -->
<!--          xaxis = list(title = "Nr. of iterations"), -->
<!--          yaxis = list(title = "Auto-correlation (at lag 1)")) -->
<!-- ``` -->

<!-- # Discussion -->
